Get CRediT

### 2022-11-19 RR_manuscript/Draft_RR.tex
add author affiliations

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H. Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E. Alotaibi\affilnum{}, Mohammed K. AlShakhori\affilnum{}, Ruth M. Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M. Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J. Beier\affilnum{}, Gabriela M. Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P. BensonMeyer\affilnum{}, Nina R. Benway\affilnum{}, Grant M. Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A. Brown\affilnum{}, Alicia M. Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M. Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L. Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A. Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M. Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K. Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L. Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S. Grose-Hodge\affilnum{}, Amelia J. Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I. Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G. Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N. Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C. Kelley\affilnum{}, Niamh E. Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A. Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O. Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M. Lima Jr.\affilnum{}, Justin J. H. Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G. S. Nogueira\affilnum{}, Heather M. Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J. Perry\affilnum{}, Alexandra M. Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P. Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A. Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V. Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J. Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J. Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B. Roettger\affilnum{4}}

\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}

>>>>

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Simon Roessig\affilnum{4}, Michael Franke\affilnum{5}, Byron Ahn\affilnum{6}, Ali H. Al-Hoorie\affilnum{7}, Jalal Al-Tamimi\affilnum{8}, Najd E. Alotaibi\affilnum{9}, Mohammed K. AlShakhori\affilnum{10}, Ruth M. Altmiller\affilnum{11}, Pablo Arantes\affilnum{12}, Angeliki Athanasopoulou\affilnum{13}, Melissa M. Baese-Berk\affilnum{14}, George Bailey\affilnum{15}, Cheman Baira A Sangma\affilnum{16}, Eleonora J. Beier\affilnum{17}, Gabriela M. Benavides\affilnum{18}, Nicole Benker\affilnum{19}, Emelia P. BensonMeyer\affilnum{20}, Nina R. Benway\affilnum{21}, Grant M. Berry\affilnum{22}, Liwen Bing\affilnum{23}, Christina Bjorndahl\affilnum{24}, Mariska Bolyanatz\affilnum{25}, Aaron Braver\affilnum{26}, Violet A. Brown\affilnum{27}, Alicia M. Brown\affilnum{28}, Alejna Brugos\affilnum{29}, Erin M. Buchanan\affilnum{30}, Tanna Butlin\affilnum{31}, Andrés Buxó-Lugo\affilnum{32}, Coline Caillol\affilnum{33}, Francesco Cangemi\affilnum{34}, Christopher Carignan\affilnum{35}, Sita Carraturo\affilnum{36}, Tiphaine Caudrelier\affilnum{37}, Eleanor Chodroff\affilnum{38}, Michelle Cohn\affilnum{39}, Johanna Cronenberg\affilnum{40}, Olivier Crouzet\affilnum{41}, Erica L. Dagar\affilnum{42}, Charlotte Dawson\affilnum{43}, Carissa A. Diantoro\affilnum{44}, Marie Dokovova\affilnum{45}, Shiloh Drake\affilnum{46}, Fengting Du\affilnum{47}, Margaux Dubuis\affilnum{48}, Florent Duême\affilnum{49}, Matthew Durward\affilnum{50}, Ander Egurtzegi\affilnum{51}, Mahmoud M. Elsherif\affilnum{52}, Janina Esser\affilnum{53}, Emmanuel Ferragne\affilnum{54}, Fernanda Ferreira\affilnum{55}, Lauren K. Fink\affilnum{56}, Sara Finley\affilnum{57}, Kurtis Foster\affilnum{58}, Paul Foulkes\affilnum{59}, Rosa Franzke\affilnum{60}, Gabriel Frazer-McKee\affilnum{61}, Robert Fromont\affilnum{62}, Christina García\affilnum{63}, Jason Geller\affilnum{64}, Camille L. Grasso\affilnum{65}, Pia Greca\affilnum{66}, Martine Grice\affilnum{67}, Magdalena S. Grose-Hodge\affilnum{68}, Amelia J. Gully\affilnum{69}, Caitlin Halfacre\affilnum{70}, Ivy Hauser\affilnum{71}, Jen Hay\affilnum{72}, Robert Haywood\affilnum{73}, Sam Hellmuth\affilnum{74}, Allison I. Hilger\affilnum{75}, Nicole Holliday\affilnum{76}, Damar Hoogland\affilnum{77}, Yaqian Huang\affilnum{78}, Vincent Hughes\affilnum{79}, Ane Icardo Isasa\affilnum{80}, Zlatomira G. Ilchovska\affilnum{81}, Hae-Sung Jeon\affilnum{82}, Jacq Jones\affilnum{83}, Mágat N. Junges\affilnum{84}, Stephanie Kaefer\affilnum{85}, Constantijn Kaland\affilnum{86}, Matthew C. Kelley\affilnum{87}, Niamh E. Kelly\affilnum{88}, Thomas Kettig\affilnum{89}, Ghada Khattab\affilnum{90}, Ruud Koolen\affilnum{91}, Emiel Krahmer\affilnum{92}, Dorota Krajewska\affilnum{93}, Andreas Krug\affilnum{94}, Abhilasha A. Kumar\affilnum{95}, Anna Lander\affilnum{96}, Tomas O. Lentz\affilnum{97}, Wanyin Li\affilnum{98}, Yanyu Li\affilnum{99}, Maria Lialiou\affilnum{100}, Ronaldo M. Lima Jr.\affilnum{101}, Justin J. H. Lo\affilnum{102}, Julio Cesar Lopez Otero\affilnum{103}, Bradley Mackay\affilnum{104}, Bethany MacLeod\affilnum{105}, Mel Mallard\affilnum{106}, Carol-Ann Mary McConnellogue\affilnum{107}, George Moroz\affilnum{108}, Mridhula Murali\affilnum{109}, Ladislas Nalborczyk\affilnum{110}, Filip Nenadić\affilnum{111}, Jessica Nieder\affilnum{112}, Dušan Nikolić\affilnum{113}, Francisco G. S. Nogueira\affilnum{114}, Heather M. Offerman\affilnum{115}, Elisa Passoni\affilnum{116}, Maud Pélissier\affilnum{117}, Scott J. Perry\affilnum{118}, Alexandra M. Pfiffner\affilnum{119}, Michael Proctor\affilnum{120}, Ryan Rhodes\affilnum{121}, Nicole Rodríguez\affilnum{122}, Elizabeth Roepke\affilnum{123}, Jan P. Röer\affilnum{124}, Lucia Sbacco\affilnum{125}, Rebecca Scarborough\affilnum{126}, Felix Schaeffler\affilnum{127}, Erik Schleef\affilnum{128}, Dominic Schmitz\affilnum{129}, Alexander Shiryaev\affilnum{130}, Márton Sóskuthy\affilnum{131}, Malin Spaniol\affilnum{132}, Joseph A. Stanley\affilnum{133}, Alyssa Strickler\affilnum{134}, Alessandro Tavano\affilnum{135}, Fabian Tomaschek\affilnum{136}, Benjamin V. Tucker\affilnum{137}, Rory Turnbull\affilnum{138}, Kingsley O. Ugwuanyi\affilnum{139}, Iñigo Urrestarazu-Porta\affilnum{140}, Ruben van de Vijver\affilnum{141}, Kristin J. Van Engen\affilnum{142}, Emiel van Miltenburg\affilnum{143}, Bruce Wang\affilnum{144}, Natasha Warner\affilnum{145}, Simon Wehrle\affilnum{146}, Hans Westerbeek\affilnum{147}, Seth Wiener\affilnum{148}, Stephen Winters\affilnum{149}, Sidney G.-J. Wong\affilnum{150}, Anna Wood\affilnum{151}, Jane Wottawa\affilnum{152}, Chenzi Xu\affilnum{153}, Germán Zárate-Sández\affilnum{154}, Georgia Zellou\affilnum{155}, Cong Zhang\affilnum{156}, Jian Zhu\affilnum{157}, Timo B. Roettger\affilnum{158}}

\affiliation{\affilnum{1, 2}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{4}{Department of Linguistics, Cornell University, United States}\\\affilnum{5}{Department of General and Computational Linguistics, University of Tübingen, Germany}\\\affilnum{6}{Program in Linguistics, Princeton University, United States}\\\affilnum{7}{Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia}\\\affilnum{8}{Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France}\\\affilnum{9}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{10}{Department of Linguistics, University of Arizona, United States}\\\affilnum{11}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{12}{Departamento de Letras, Universidade Federal de São Carlos, Brazil}\\\affilnum{13}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{14}{Department of Linguistics, University of Oregon, United States}\\\affilnum{15}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{16}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{17}{Department of Psychology, University of California, Davis, United States}\\\affilnum{18}{Department of Linguistics, University of Arizona, United States}\\\affilnum{19}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{20}{NA, University of Pennsylvania, United States}\\\affilnum{21}{Department of Communication Sciences and Disorders, Syracuse University, United States}\\\affilnum{22}{Department of Spanish, Villanova University, United States}\\\affilnum{23}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{24}{Department of Philosophy, Carnegie Mellon University, United States}\\\affilnum{25}{Department of Spanish \& French Studies, Occidental College, United States}\\\affilnum{26}{Department of English, Texas Tech University, United States}\\\affilnum{27}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{28}{Department of Spanish and Portuguese, University of Arizona, United States}\\\affilnum{29}{Division of Mathematics and Computer Science, Simmons University, United States}\\\affilnum{30}{Analytics, Harrisburg University of Science and Technology, United States}\\\affilnum{31}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{32}{Department of Psychology, University at Buffalo, SUNY, United States}\\\affilnum{33}{Université Paris Cité, France}\\\affilnum{34}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{35}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{36}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{37}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{38}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{39}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{40}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{41}{LLING, UMR6310, Nantes Université / CNRS, France}\\\affilnum{42}{Department of Linguisticss and TESOL, University of Texas at Arlington, United States}\\\affilnum{43}{School of Psychology, Newcastle University, United Kingdom}\\\affilnum{44}{Department of Linguistics, University of Oregon, United States}\\\affilnum{45}{School of Psychological Sciences and Health, University of Strathclyde, United Kingdom}\\\affilnum{46}{Department of Linguistics, University of Oregon, United States}\\\affilnum{47}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{48}{Department of comparative language science, Universität Zürich, Swizerland, Switzerland}\\\affilnum{49}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{50}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{51}{IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{52}{Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom}\\\affilnum{53}{Statistics Group, Association for Diversity in Linguistics, Germany}\\\affilnum{54}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{55}{Department of Psychology, University of California, Davis, United States}\\\affilnum{56}{Department of Music, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{57}{Department of Psychology, Pacific Lutheran University, United States}\\\affilnum{58}{Department of Linguistics, University of Oregon, United States}\\\affilnum{59}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{60}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{61}{Department of languages, linguistics, and translation, Université Laval, Canada}\\\affilnum{62}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{63}{Department of Languages, Literatures, and Cultures, Saint Louis University, United States}\\\affilnum{64}{Department of Psychology, Princeton University, United States}\\\affilnum{65}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{66}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{67}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{68}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{69}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{70}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{71}{Department of Linguistics and TESOL, University of Texas at Arlington, United States}\\\affilnum{72}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{73}{Ao Tawhiti Unlimited Discovery, New Zealand}\\\affilnum{74}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{75}{Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States}\\\affilnum{76}{Department of Linguistics and Cognitive Science, Pomona College, United States}\\\affilnum{77}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{78}{University of California, Los Angeles, United States}\\\affilnum{79}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{80}{Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States}\\\affilnum{81}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{82}{School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom}\\\affilnum{83}{Department of Linguistics, University of Canterbury, Aotearoa}\\\affilnum{84}{Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil}\\\affilnum{85}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{86}{Institute of Linguistics, University of Cologne, Germany}\\\affilnum{87}{Department of Linguistics, University of Washington, United States}\\\affilnum{88}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{89}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{90}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{91}{Department of Communication and Cognition, Tilburg University, Netherlands}\\\affilnum{92}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{93}{Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain}\\\affilnum{94}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{95}{Department of Psychology, Bowdoin College, ME, United States}\\\affilnum{96}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{97}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{98}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{99}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{100}{Institute of German Language I Linguistics, University of Cologne, Germany}\\\affilnum{101}{Department of English Language Studies, Federal University of Ceará, Brazil}\\\affilnum{102}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{103}{Department of Hispanic Studies, University of Houston, United States}\\\affilnum{104}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{105}{School of Linguistics \& Language Studies, Carleton University, Canada}\\\affilnum{106}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{107}{Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom}\\\affilnum{108}{HSE University, Russia}\\\affilnum{109}{Speech and Language Therapy, University of Strathclyde, United Kingdom}\\\affilnum{110}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{111}{Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia}\\\affilnum{112}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{113}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{114}{Graduate Program in Linguistics, Federal University of Ceará, Brazil}\\\affilnum{115}{World Languages, Literatures and Cultures Department, University of Arkansas, United States}\\\affilnum{116}{Deparment of Linguistics, Queen Mary University of London, United Kingdom}\\\affilnum{117}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{118}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{119}{Department of Linguistics, University of California, Berkeley, United States}\\\affilnum{120}{Department of Linguistics, Macquarie University, Australia}\\\affilnum{121}{Center for Cognitive Science, Rutgers University, United States}\\\affilnum{122}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{123}{Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States}\\\affilnum{124}{Department of Psychology, Witten/Herdecke University, Germany}\\\affilnum{125}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{126}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{127}{Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom}\\\affilnum{128}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{129}{Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany}\\\affilnum{130}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{131}{Department of Linguistics, University of British Columbia, Canada}\\\affilnum{132}{Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany}\\\affilnum{133}{Department of Linguistics, Brigham Young University, United States}\\\affilnum{134}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{135}{Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{136}{Department of General Linguistics, University of Tübingen, Germany}\\\affilnum{137}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{138}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{139}{Department of English \& Literary Studies, University of Nigeria, Nsukka, Nigeria}\\\affilnum{140}{IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{141}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{142}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{143}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{144}{Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China}\\\affilnum{145}{Department of Linguistics, University of Arizona, United States}\\\affilnum{146}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{147}{Department of Languages, Literature and Communication, Utrecht University, Netherlands}\\\affilnum{148}{Department of Modern Languages, Carnegie Mellon University, United States}\\\affilnum{149}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{150}{Geospatial Research Institute, University of Canterbury, New Zealand}\\\affilnum{151}{Department of Linguistics, University of Oregon, United States}\\\affilnum{152}{Département de Lettres modernes, LIUM, LST, Le Mans Université, France}\\\affilnum{153}{NA, University of Oxford, United Kingdom}\\\affilnum{154}{Department of Spanish, Western Michigan University, United States}\\\affilnum{155}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{156}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{157}{School of Information, University of Michigan, Ann Arbor, United States}\\\affilnum{158}{Department of Linguistics and Scandinavian Studies, University of Oslo, Norway}}

### 2022-11-19 scripts/r/09_credit_taxonomy.Rmd
add author affiliations

```{r}
#| label: load-libs
library("googlesheets4")
library("googledrive")
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

@@

```{r}
#| label: load-tidy-csv
# Load data
#all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")
all_data_temp <- 
  read_csv("data/CRediT/MSA_tenzing_contribution-corrected_contributions.csv") %>% 
  janitor::clean_names()

@@

@@

There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
`r filter(affiliations, is.na(primary_affiliation_university)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.

@@

contributors %>% 
  select(name, primary_affiliation_university) %>% 
  transmute(
    name, 
    name_man = glue::glue("- name: {name}"), 
    num_man = glue::glue("- num: {1:nrow(.) + 1}")
  ) %>% 
  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
  pull(print) %>% 
  clipr::write_clip()

contributors %>% 
  select(name, primary_affiliation_university, primary_affiliation_department) %>% 
  transmute(
    name, 
    num_man = glue::glue("- num: {1:nrow(.) + 1}"), 
    print = glue::glue("- org: {primary_affiliation_department}, {primary_affiliation_university}"), 
  ) %>% 
  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
  pull(print) %>% 
  clipr::write_clip() 
```

>>>>

```{r}
#| label: load-libs
library("googlesheets4")
library("googledrive")
library("xml2")
library("dplyr")
library("tidyr")
library("glue")
library("stringr")
library("ggplot2")
library("ggtext")
library("forcats")
library("readr")
library("kableExtra")
library("countrycode")
```

@@

```{r}
#| label: load-tidy-csv
# Load data
#all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")
all_data_temp <- 
  read_csv("data/CRediT/MSA_tenzing_contribution-corrected_contributions.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    primary_affiliation_country = if_else(
      primary_affiliation_country == "Aotearoa", 
      "New Zealand", 
      .$primary_affiliation_country
      ), 
    cntry = countrycode(
      primary_affiliation_country, 
      origin = 'country.name', 
      destination = 'iso3c'
      ), 
    flag = countrycode(
      cntry, 
      origin = 'iso3c', 
      destination = 'unicode.symbol')
    )

@@

n_no_affiliation <- sum(is.na(contributors$primary_affiliation_university))

@@

There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
`r n_no_affiliation %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.

## Countries

```{r}
#| label: analysts-by-country

open <- "<img src="
close <- " width='25' /><br>"

n_countries <- contributors %>% 
  count(primary_affiliation_country, flag) %>% 
  arrange(n) %>% 
  mutate(
    country = primary_affiliation_country, 
    labs = case_when(
      country == "Australia" ~ glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
      country == "Hong Kong SAR, China" ~ glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
      country == "Nigeria" ~ glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
      country == "Norway" ~ glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
      country == "Saudi Arabia" ~ glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
      country == "Serbia" ~ glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
      country == "Switzerland" ~ glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
      country == "Austria" ~ glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
      country == "Russia" ~ glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
      country == "Spain" ~ glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
      country == "Brazil" ~ glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
      country == "Netherlands" ~ glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
      country == "New Zealand" ~ glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
      country == "Canada" ~ glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
      country == "France" ~ glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
      country == "Germany" ~ glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
      country == "United Kingdom" ~ glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
      country == "United States" ~ glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
    ), 
    primary_affiliation_country = fct_reorder(primary_affiliation_country, n, max))

n_countries %>% 
  ggplot() + 
  aes(x = n, y = primary_affiliation_country) + 
  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
  geom_point() + 
  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
  theme_bw(base_size = 9) + 
  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
  theme(axis.text.y = element_markdown(color = "black"))

@@

contributors %>% 
  select(name, 
         primary_affiliation_department, 
         primary_affiliation_university, 
         primary_affiliation_country) %>% 
  transmute(
    name, 
    name_man = glue::glue("- name: {name}"), 
    num_man = glue::glue("- num: {1:nrow(.) + 1}")
  ) %>% 
  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
  pull(print) %>% 
  clipr::write_clip()

contributors %>% 
  select(name, 
         primary_affiliation_department, 
         primary_affiliation_university, 
         primary_affiliation_country) %>% 
  transmute(
    name, 
    num_man = glue::glue("- num: {1:nrow(.) + 1}"), 
    print = glue::glue("- org: {primary_affiliation_department}, {primary_affiliation_university}, {primary_affiliation_country}"), 
  ) %>% 
  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
  pull(print) %>% 
  clipr::write_clip() 
```
